Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-06 cmsb22.tex
Add responses, add a small change in Section "Conclusion"

\vangiang{n = 431 comes from Table 1 of~\cite{aghamiri2020automated}. I have checked this model. It has only 180 nodes. I will check others models come from~\cite{aghamiri2020automated}.}
\sylvain{that's actually another model (called RA-map or something in the supplementary material), I think the other models should be ok.}

@@

    adhesion-cip-migration-cell-cycle~\cite{guberman2020boolean} & 121 & 493 & 4 & - & - & 78 & 3.72 \\
    interferon-1~\cite{ostaszewski2021covid19} & 121 & 190 & 55 & - & - & 512 & 0.43 \\
    TCR-TLR5-signaling-2018~\cite{rodriguez2019cooperation} & 130 & 273 & 2 & - & - & 48 & 0.50 \\
    influenza-virus-replication-cycle~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 131 & 302 & 11 & - & - & 2560 & 1.07 \\
    signaling-in-prostate-cancer~\cite{Montagud2021} & 133 & 431 & 0 & - & - & 812 & 1.40 \\
    HIV-1-with-T-cell-signaling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 138 & 368 & 14 & DNF & DNF & 1408 & 1.44 \\
    signal-transduction-in-fibroblasts~\cite{helikar2008emergent} & 139 & 557 & 9 & - & - & 375850 & 331.87 \\
    HMOX-1-pathway~\cite{ostaszewski2021covid19} & 145 & 228 & 56 & - & - & 5120 & 0.99 \\
    kynurenine-pathway~\cite{ostaszewski2021covid19} & 150 & 304 & 72 & - & - & 512 & 3.79 \\
    virus-replication-cycle~\cite{ostaszewski2021covid19} & 154 & 268 & 25 & - & - & 1024 & 0.67 \\
    immune-system~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 164 & 506 & 13 & DNF & DNF & 36852 & 14.19 \\
    er-stress~\cite{ostaszewski2021covid19} & 182 & 266 & 75 & - & - & 25600 & 4.54 \\
    cascade-3~\cite{Tsirvouli2020} & 183 & 603 & 0 & - & - & 1 & 1.65 \\
    CHO-2016~\cite{lee2019signal} & 200 & 696 & 13 & - & - & 1024 & 2.10 \\ \midrule

    T-cell-check-point~\cite{hernandez2020computational} & 218 & - & 34 & - & - & 15360 & 4.33 \\
    ErbB-receptor-signaling~\cite{helikar2013comprehensive} & 247 & 1100 & 22 & DNF & DNF & DNF & DNF \\
    signaling-macrophage-activation~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 321 & 533 & 19 & - & - & 512 & 1.58 \\
    cholocystokinin~\cite{aghamiri2020automated} & 404 & - & 95 & - & - & 705024 & 1080.35 \\
    RA-apoptosis~\cite{aghamiri2020automated} & 431 & - & 59 & DNF & DNF & 640 & 0.70 \\ \midrule

@@

\sylvain{the \texttt{dom-pref} thing is deprecated since 2014 but still used in PyBoolNet, I think we might give the more modern version I used in the Python script, but we'll see}
\vangiang{I also found that you did not use the \texttt{dom-pref} thing in the Python script. I think we should use the same configuration as that used in PyBoolNet.}
\sylvain{as said above, this is deprecated, and has been since August 2014 \url{https://github.com/potassco/clasp/blob/master/CHANGES}, so I'd advise against using it, it might break any-time.}

@@

Moreover, there are other methods for the maximal siphon computation, like SAT/MaxSAT approaches~\cite{nabli2016enumerating} that could replace our ASP program if they outperform it.

>>>>

\vangiang{n = 431 comes from Table 1 of~\cite{aghamiri2020automated}. I have checked this model. It has only 180 nodes. I will check others models come from~\cite{aghamiri2020automated}.}
\sylvain{that's actually another model (called RA-map or something in the supplementary material), I think the other models should be ok.}
\vangiang{Oh. Thank you for confirming that.}

@@

    adhesion-cip-migration-cell-cycle~\cite{guberman2020boolean} & 121 & 493 & 4 & - & - & 78 & 3.72 \\
    interferon-1~\cite{ostaszewski2021covid19} & 121 & 190 & 55 & - & - & 512 & 0.43 \\
    TCR-TLR5-signaling-2018~\cite{rodriguez2019cooperation} & 130 & 273 & 2 & - & - & 48 & 0.50 \\
    influenza-virus-replication-cycle~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 131 & 302 & 11 & - & - & 2560 & 1.07 \\
    signaling-in-prostate-cancer~\cite{Montagud2021} & 133 & 431 & 0 & - & - & 812 & 1.40 \\
    HIV-1-with-T-cell-signaling~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 138 & 368 & 14 & DNF & DNF & 1408 & 1.44 \\
    signal-transduction-in-fibroblasts~\cite{helikar2008emergent} & 139 & 557 & 9 & - & - & 375850 & 331.87 \\
    HMOX-1-pathway~\cite{ostaszewski2021covid19} & 145 & 228 & 56 & - & - & 5120 & 0.99 \\
    kynurenine-pathway~\cite{ostaszewski2021covid19} & 150 & 304 & 72 & - & - & 512 & 3.79 \\
    virus-replication-cycle~\cite{ostaszewski2021covid19} & 154 & 268 & 25 & - & - & 1024 & 0.67 \\
    immune-system~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 164 & 506 & 13 & DNF & DNF & 36852 & 14.19 \\
    RA-apoptosis~\cite{aghamiri2020automated} & 181 & - & 59 & DNF & DNF & 640 & 0.70 \\
    er-stress~\cite{ostaszewski2021covid19} & 182 & 266 & 75 & - & - & 25600 & 4.54 \\
    cascade-3~\cite{Tsirvouli2020} & 183 & 603 & 0 & - & - & 1 & 1.65 \\
    CHO-2016~\cite{lee2019signal} & 200 & 696 & 13 & - & - & 1024 & 2.10 \\ \midrule

    T-cell-check-point~\cite{hernandez2020computational} & 218 & - & 34 & - & - & 15360 & 4.33 \\
    ErbB-receptor-signaling~\cite{helikar2013comprehensive} & 247 & 1100 & 22 & DNF & DNF & DNF & DNF \\
    signaling-macrophage-activation~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 321 & 533 & 19 & - & - & 512 & 1.58 \\
    cholocystokinin~\cite{aghamiri2020automated} & 404 & - & 95 & - & - & 705024 & 1080.35 \\ \midrule

@@

\sylvain{the \texttt{dom-pref} thing is deprecated since 2014 but still used in PyBoolNet, I think we might give the more modern version I used in the Python script, but we'll see}
\vangiang{I also found that you did not use the \texttt{dom-pref} thing in the Python script. I think we should use the same configuration as that used in PyBoolNet.}
\sylvain{as said above, this is deprecated, and has been since August 2014 \url{https://github.com/potassco/clasp/blob/master/CHANGES}, so I'd advise against using it, it might break any-time.}
\vangiang{I see. Let's use the more modern version.}

@@

Moreover, there are possibly other methods for the maximal siphon computation, like SAT/MaxSAT approaches~\cite{nabli2016enumerating}. We also plan to investigate them in the future. They could replace our ASP program if they outperform it.
